Anisotropic in-plane thermal conductivity in multilayer silicene

### 2018-01-11 latex/paper.tex
将2l1改为2L1

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2018-01-11 00:20:31

@@

The surface reconstruction has substantial influence on thermal conductivity of multilayer silicene.
Fig.\ref{fig:tc_length_sheng}(a) presents the length dependence of thermal conductivity of three structures of bilayer silicene.
One can see that the thermal conductivity converges quickly with cutoff phonon mean free path (MFP) in of 2l2 structure, while it is a bit slowly in 2l1 and 2l3 structures. Also, the cutoff MFPs of 2l1 structure are distinct in the armchair and zigzag directions. These features can be attributed to the different scattering intensity caused by the surface reconstructions.
It is known that the ballistic phonon transport is dominating when the length of the sample is smaller than the MFP,  whereas the diffuse phonon transport is  dominating when the length is larger than the MFP.
An empirical formula had been proposed by Thomas\cite{Thomas2010}  to characterize the thermal conductivity from ballistic to diffuse phonon-transport region, which is
\begin{equation}
  \kappa = \kappa_\infty (1-e^{-\frac{L}{L_c}}) \label{eq:eq_nemd}
\end{equation}
where $\kappa_\infty$ is the fitted full scattering thermal conductivity, $L_c$ is the transition length from the ballistic transportation to the diffuse transportation. Here we find that the length dependence of thermal conductivity of multilayer silicene can also be well described by such formula.
The saturated thermal conductivity of 2l1 structure reaches up to 42.1 (57.9) W/mK, while it is  31.1 (31.1) W/mK  for 2l2 structure and  3.3 (5.6)  W/mK for 2l3 structure in zigzag (armchair) direction, respectively,  showing the significant influence of surface reconstruction on thermal conductivity.

The surface reconstruction also induces thermal conductivity anisotropy. The anisotropy can be presented by
\begin{equation}
  \chi=\frac{|\kappa_{z,\infty}-\kappa_{a,\infty} |}{ max⁡(\kappa_{z,\infty}-\kappa_{a,\infty} ) } \times 100 \%  \label{eq:eq_chi}
\end{equation}
with $ \kappa_{z,\infty} (\kappa_{a,\infty})$ being the full scattering thermal conductivity (infinite thermal conductivity) in the zigzag (armchair) direction.
It is found that both 2l2 and 2l3 structures show large thermal conductivity anisotropy, i.e., 27\% and 41\%, respectively, while 2l2 structure does not exhibits the anisotropy owning to its rotational symmetry over $\pi/2$.  The ultra-low and particularly high thermal conductivity anisotropy of bilayer silicene indicate its potential applications in the nanoelectronics.

\begin{figure}[b]
  \includegraphics[angle= 0, width=0.9\linewidth]{images/tc_length_sheng.eps}
  \caption{\label{fig:tc_length_sheng} (color online) The depencence of cummulative thermal conductivity(TC) on cutoff phonon mean free path for all the structures. a) The cummulative TC of bilayer silicene structures. b) The cummulative TC of multilayer silicene with $2\times 1$ reconstruction and different layer. The dots are the results from BTE calculations, and the lines are the fitted results using Eq.(\ref{eq:eq_nemd}). The letter z/a in the legend means that the transport direction is zigzag/armchair. The dots of 2l2a and 2l2z are almost the same so red solid dots are covered. With the increase of cutoff mean free path TC converges. For bilayer structures TC along armchair direction is larger while for the others TC along zigzag direction is larger. With the increase of thickness TC along zigzag decreases while that along armchair increases a little. }
\end{figure}

\begin{figure}[b]
  \includegraphics[angle= 0, width=0.9\linewidth]{images/chi.eps}{}
  \caption{\label{fig:chi} (color online) The dependence on cutoff MPF of cummulative TC anisotropy $\chi$. $\chi$ of 2l2 structure is exactly zero and is a horizonal line at 0. For 2l1, 2l3  structures the anisotropy increase with the cutoff MPF while that of 3l1 decreases. The others show indepencece of cutoff MPF. For bilayer silicence the anisotropy comes from long wave phonons while for multilayer structure it comes from phonons of all the wave length. }
\end{figure}

@@

The anisotropy shows size effect in bilayer structure while no size effect of it is found in multilayer structures. As shown in Fig.\ref{fig:chi}, the thermal conductivity of  2l1 bilayer silicene is almost isotropic with length of 10-1000 \angstrom, and it becomes increasingly anisotropic for length  above 1000  \angstrom. This is essentially due to the difference of acoustic phonons in different directions,  which have large MFP.  As for the $2\times1$ structures with 3-8 Si layers in thickness, the high thermal conductivity anisotropy is obtained even when the length is as short as 10 \angstrom, implying that the anisotropy is  mainly induced by the optical phonons. On the other hand, the thermal conductivity anisotropy of 2l3 silicene can be owning to both acoustic and  optical phonons in different directions.

\begin{table*}
  \caption{\label{tab:table1}
    The thermal conductivity and its anisotropy of different multilayer silicene, along with the average heat capacity ($kJ/m^3/K$) of zigzag ( $Cv_z$) and armchair ($Cv_a$) directions, respectively. }
  \begin{ruledtabular}
    \begin{tabular}{ccccccc}
          & Minimal period
          & $\kappa_{z,\infty}$
          & $\kappa_{a,\infty}$
          & $\chi$
          & $Cv_{z}$
          & $Cv_{a}$                                                           \\
      \hline
      2l1 & $1 \times 1$             & 42.10 & 57.92 & 27.31\% & 165.8 & 166.7 \\
      2l2 & $\sqrt{2}\times\sqrt{2}$ & 31.11 & 31.11 & 0    \% & 38.44 & 38.44 \\
      2l3 & $2 \times 2$             & 3.311 & 5.624 & 41.13\% & 22.42 & 22.42 \\
      3l1 & $2 \times 1$             & 31.44 & 14.05 & 55.29\% & 52.22 & 52.46 \\
      4l1 & $2 \times 1$             & 20.37 & 6.114 & 69.98\% & 37.71 & 37.89 \\
      5l1 & $2 \times 1$             & 19.33 & 6.419 & 66.78\% & 29.17 & 29.32 \\
      6l1 & $2 \times 1$             & 17.78 & 6.527 & 63.29\% & 23.73 & 23.86 \\
      8l1 & $2 \times 1$             & 17.56 & 7.461 & 57.51\% & 17.26 & 17.36 \\
    \end{tabular}
  \end{ruledtabular}
\end{table*}

The magnitude and anisotropy of TC is mainly contributed from low frequency phonons in bilayers structures while that in multilayer structures comes from high frequency phonons. To explore the origin of thermal conductivity anisotropy, we have calculated the phonon frequency distributions of thermal conductivity in armchair and zigzag directions  (Fig.\ref{fig:tc_freq}).
It is found that the anisotropy is mainly attributed to the low-frequency (0-5 THz) phonons for the bilayer silicene, i. e., 2l1 and 2l3, where thermal conductivity in armchair direction is obviously larger than that in zigzag direction.
Whereas,  for the $2\times1$ structures thicker than 3 Si layers, the thermal conductivities in armchair and zigzag directions are nearly the same in the low-frequency region, and the anisotropy is mainly attributed to the high-frequency (5-20 THz) phonons.
In addition, the anisotropy of the 3l1 structure is resulted by the phonons with frequency above 10 THz, below which the summation of contributions to thermal conductivity are nearly the same in armchair and zigzag directions.

@@

\begin{figure}[b]
  \includegraphics[width=1\linewidth]{images/tau.eps}
  \caption{\label{fig:tau} (color online)  Phonons lifetimes of multilayer silicene obtained by considering the three-phonon scattering process.  The horizonal dash line at 1.0ps is a guidence for the main contribution region of phonon frequency. Phonon lifetime doent's show obvious anisotropy in both bilayer structure and multilayer structures (except for the anmornal region of 5-7 THz in 4l1 structure). The main contribution of lifetime comes from low frequency phonons in bilayer structures while the others have relative uniform contribution from the frequency domain.  }
\end{figure}

@@

Phonon lifetime of low frequency is much larger and anisotropic than high frequency in bilayer structures while in multilayer structures it has less denpendence on frequency. We have considered the three-phonon scattering process, where the scattering rate is obtained from the Fermi-golden's rule\cite{Li2014} under the relaxation time approximation (RTA). The iterative method was then adopted to include the cross influence of the phonon excitation, since it usually gives lager but more accurate lifetimes than the RTA. The frequency dependence of phonon lifetimes calculated with ShengBTE\cite{Li2014} are shown in Fig.\ref{fig:tau}, where the values are averaged for frequency bins to reduce complexity.  It is shown that the lifetimes of larger than 1 ps for bilayer silicene structures (2l1, 2l3) distribute on the low-frequency region, indicating the dominating contributions of low-frequency phonons to the thermal conductivity. Moreover, the lifetimes in armchair direction are obviously larger than that in zigzag direction in the low-frequency region. This feature indicates that the thermal conductivity anisotropy of bilayer silicene is attributed to the difference of phonon lifetimes in different directions.
On the other hand, the phonon lifetimes exhibit a different frequency distribution for the thicker silicene, i. e.,  $2\times1$ structures with 3-6 Si layer in thickness, where the phonon lifetimes larger than 1 ps cover both the low and high frequency regions.  This explains why the high frequency phonons contribute significantly to the thermal conductivity in the thicker silicene (Fig. \ref{fig:tc_freq}).  However, except for the 4l1 structure, the phonon lifetimes in zigzag and armchair directions are very close for the $2\times1$ structures, implying their tiny effect on the thermal conductivity anisotropy.

Group velocity at low frequency shows no anisotropy in bilayer structures while that of zigzag direction is larger than that of armchair direction in 3-6 layer structures. As shown in Fig. \ref{fig:gv},  the group-velocity difference in the two directions is very small in the low-frequency region for the bilayer silicene. This result confirms that the thermal conductivity anisotropy mainly comes from the different phonon scatterings in the armchair and zigzag directions,  which induce different phonon lifetimes.
As for the $2\times 1$ silicene with thickness more than three Si layers,  the group velocity in zigzag direction is obviously larger than that in the armchair direction in most of the frequency region. Considering that the phonon-lifetime difference contributes little to the anisotropy for 3l1, 5l1, and 6l1 structures, one can conclude that the group velocity difference is the main reason for the thermal conductivity anisotropy of $2\times 1$ multilayer silicene. It should be noted that the anisotropy of 4l1 structure is from the contributions of both phonon lifetime and group velocity, which lead to its unusual large anisotropy up to 70\%.

>>>>

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2018-01-11 15:12:52

@@

The surface reconstruction has substantial influence on thermal conductivity of multilayer silicene.
Fig.\ref{fig:tc_length_sheng}(a) presents the length dependence of thermal conductivity of three structures of bilayer silicene.
One can see that the thermal conductivity converges quickly with cutoff phonon mean free path (MFP) in of 2L2 structure, while it is a bit slowly in 2L1 and 2L3 structures. Also, the cutoff MFPs of 2L1 structure are distinct in the armchair and zigzag directions. These features can be attributed to the different scattering intensity caused by the surface reconstructions.
It is known that the ballistic phonon transport is dominating when the length of the sample is smaller than the MFP,  whereas the diffuse phonon transport is  dominating when the length is larger than the MFP.
An empirical formula had been proposed by Thomas\cite{Thomas2010}  to characterize the thermal conductivity from ballistic to diffuse phonon-transport region, which is
\begin{equation}
  \kappa = \kappa_\infty (1-e^{-\frac{L}{L_c}}) \label{eq:eq_nemd}
\end{equation}
where $\kappa_\infty$ is the fitted full scattering thermal conductivity, $L_c$ is the transition length from the ballistic transportation to the diffuse transportation. Here we find that the length dependence of thermal conductivity of multilayer silicene can also be well described by such formula.
The saturated thermal conductivity of 2L1 structure reaches up to 42.1 (57.9) W/mK, while it is  31.1 (31.1) W/mK  for 2L2 structure and  3.3 (5.6)  W/mK for 2L3 structure in zigzag (armchair) direction, respectively,  showing the significant influence of surface reconstruction on thermal conductivity.

The surface reconstruction also induces thermal conductivity anisotropy. The anisotropy can be presented by
\begin{equation}
  \chi=\frac{|\kappa_{z,\infty}-\kappa_{a,\infty} |}{ max⁡(\kappa_{z,\infty}-\kappa_{a,\infty} ) } \times 100 \%  \label{eq:eq_chi}
\end{equation}
with $ \kappa_{z,\infty} (\kappa_{a,\infty})$ being the full scattering thermal conductivity (infinite thermal conductivity) in the zigzag (armchair) direction.
It is found that both 2L2 and 2L3 structures show large thermal conductivity anisotropy, i.e., 27\% and 41\%, respectively, while 2L2 structure does not exhibits the anisotropy owning to its rotational symmetry over $\pi/2$.  The ultra-low and particularly high thermal conductivity anisotropy of bilayer silicene indicate its potential applications in the nanoelectronics.

\begin{figure}[b]
  \includegraphics[angle= 0, width=0.9\linewidth]{images/tc_length_sheng.eps}
  \caption{\label{fig:tc_length_sheng} (color online) The depencence of cummulative thermal conductivity(TC) on cutoff phonon mean free path for all the structures. a) The cummulative TC of bilayer silicene structures. b) The cummulative TC of multilayer silicene with $2\times 1$ reconstruction and different layer. The dots are the results from BTE calculations, and the lines are the fitted results using Eq.(\ref{eq:eq_nemd}). The letter z/a in the legend means that the transport direction is zigzag/armchair. The dots of 2L2a and 2L2z are almost the same so red solid dots are covered. With the increase of cutoff mean free path TC converges. For bilayer structures TC along armchair direction is larger while for the others TC along zigzag direction is larger. With the increase of thickness TC along zigzag decreases while that along armchair increases a little. }
\end{figure}

\begin{figure}[b]
  \includegraphics[angle= 0, width=0.9\linewidth]{images/chi.eps}{}
  \caption{\label{fig:chi} (color online) The dependence on cutoff MPF of cummulative TC anisotropy $\chi$. $\chi$ of 2L2 structure is exactly zero and is a horizonal line at 0. For 2L1, 2L3  structures the anisotropy increase with the cutoff MPF while that of 3L1 decreases. The others show indepencece of cutoff MPF. For bilayer silicence the anisotropy comes from long wave phonons while for multilayer structure it comes from phonons of all the wave length. }
\end{figure}

@@

The anisotropy shows size effect in bilayer structure while no size effect of it is found in multilayer structures. As shown in Fig.\ref{fig:chi}, the thermal conductivity of  2L1 bilayer silicene is almost isotropic with length of 10-1000 \angstrom, and it becomes increasingly anisotropic for length  above 1000  \angstrom. This is essentially due to the difference of acoustic phonons in different directions,  which have large MFP.  As for the $2\times1$ structures with 3-8 Si layers in thickness, the high thermal conductivity anisotropy is obtained even when the length is as short as 10 \angstrom, implying that the anisotropy is  mainly induced by the optical phonons. On the other hand, the thermal conductivity anisotropy of 2L3 silicene can be owning to both acoustic and  optical phonons in different directions.

\begin{table*}
  \caption{\label{tab:table1}
    The thermal conductivity and its anisotropy of different multilayer silicene, along with the average heat capacity ($kJ/m^3/K$) of zigzag ( $Cv_z$) and armchair ($Cv_a$) directions, respectively. }
  \begin{ruledtabular}
    \begin{tabular}{ccccccc}
          & Minimal period
          & $\kappa_{z,\infty}$
          & $\kappa_{a,\infty}$
          & $\chi$
          & $Cv_{z}$
          & $Cv_{a}$                                                           \\
      \hline
      2L1 & $1 \times 1$             & 42.10 & 57.92 & 27.31\% & 165.8 & 166.7 \\
      2L2 & $\sqrt{2}\times\sqrt{2}$ & 31.11 & 31.11 & 0    \% & 38.44 & 38.44 \\
      2L3 & $2 \times 2$             & 3.311 & 5.624 & 41.13\% & 22.42 & 22.42 \\
      3L1 & $2 \times 1$             & 31.44 & 14.05 & 55.29\% & 52.22 & 52.46 \\
      4L1 & $2 \times 1$             & 20.37 & 6.114 & 69.98\% & 37.71 & 37.89 \\
      5L1 & $2 \times 1$             & 19.33 & 6.419 & 66.78\% & 29.17 & 29.32 \\
      6L1 & $2 \times 1$             & 17.78 & 6.527 & 63.29\% & 23.73 & 23.86 \\
      8L1 & $2 \times 1$             & 17.56 & 7.461 & 57.51\% & 17.26 & 17.36 \\
    \end{tabular}
  \end{ruledtabular}
\end{table*}

The magnitude and anisotropy of TC is mainly contributed from low frequency phonons in bilayers structures while that in multilayer structures comes from high frequency phonons. To explore the origin of thermal conductivity anisotropy, we have calculated the phonon frequency distributions of thermal conductivity in armchair and zigzag directions  (Fig.\ref{fig:tc_freq}).
It is found that the anisotropy is mainly attributed to the low-frequency (0-5 THz) phonons for the bilayer silicene, i. e., 2L1 and 2L3, where thermal conductivity in armchair direction is obviously larger than that in zigzag direction.
Whereas,  for the $2\times1$ structures thicker than 3 Si layers, the thermal conductivities in armchair and zigzag directions are nearly the same in the low-frequency region, and the anisotropy is mainly attributed to the high-frequency (5-20 THz) phonons.
In addition, the anisotropy of the 3L1 structure is resulted by the phonons with frequency above 10 THz, below which the summation of contributions to thermal conductivity are nearly the same in armchair and zigzag directions.

@@

\begin{figure}[b]
  \includegraphics[width=1\linewidth]{images/tau.eps}
  \caption{\label{fig:tau} (color online)  Phonons lifetimes of multilayer silicene obtained by considering the three-phonon scattering process.  The horizonal dash line at 1.0ps is a guidence for the main contribution region of phonon frequency. Phonon lifetime doent's show obvious anisotropy in both bilayer structure and multilayer structures (except for the anmornal region of 5-7 THz in 4L1 structure). The main contribution of lifetime comes from low frequency phonons in bilayer structures while the others have relative uniform contribution from the frequency domain.  }
\end{figure}

@@

Phonon lifetime of low frequency is much larger and anisotropic than high frequency in bilayer structures while in multilayer structures it has less denpendence on frequency. We have considered the three-phonon scattering process, where the scattering rate is obtained from the Fermi-golden's rule\cite{Li2014} under the relaxation time approximation (RTA). The iterative method was then adopted to include the cross influence of the phonon excitation, since it usually gives lager but more accurate lifetimes than the RTA. The frequency dependence of phonon lifetimes calculated with ShengBTE\cite{Li2014} are shown in Fig.\ref{fig:tau}, where the values are averaged for frequency bins to reduce complexity.  It is shown that the lifetimes of larger than 1 ps for bilayer silicene structures (2L1, 2L3) distribute on the low-frequency region, indicating the dominating contributions of low-frequency phonons to the thermal conductivity. Moreover, the lifetimes in armchair direction are obviously larger than that in zigzag direction in the low-frequency region. This feature indicates that the thermal conductivity anisotropy of bilayer silicene is attributed to the difference of phonon lifetimes in different directions.
On the other hand, the phonon lifetimes exhibit a different frequency distribution for the thicker silicene, i. e.,  $2\times1$ structures with 3-6 Si layer in thickness, where the phonon lifetimes larger than 1 ps cover both the low and high frequency regions.  This explains why the high frequency phonons contribute significantly to the thermal conductivity in the thicker silicene (Fig. \ref{fig:tc_freq}).  However, except for the 4L1 structure, the phonon lifetimes in zigzag and armchair directions are very close for the $2\times1$ structures, implying their tiny effect on the thermal conductivity anisotropy.

Group velocity at low frequency shows no anisotropy in bilayer structures while that of zigzag direction is larger than that of armchair direction in 3-6 layer structures. As shown in Fig. \ref{fig:gv},  the group-velocity difference in the two directions is very small in the low-frequency region for the bilayer silicene. This result confirms that the thermal conductivity anisotropy mainly comes from the different phonon scatterings in the armchair and zigzag directions,  which induce different phonon lifetimes.
As for the $2\times 1$ silicene with thickness more than three Si layers,  the group velocity in zigzag direction is obviously larger than that in the armchair direction in most of the frequency region. Considering that the phonon-lifetime difference contributes little to the anisotropy for 3L1, 5L1, and 6L1 structures, one can conclude that the group velocity difference is the main reason for the thermal conductivity anisotropy of $2\times 1$ multilayer silicene. It should be noted that the anisotropy of 4L1 structure is from the contributions of both phonon lifetime and group velocity, which lead to its unusual large anisotropy up to 70\%.
